Infering species distribution from aggregated spatial data

### 2022-04-02 Version_M2_plusieurszones/pres/GDREcostat_April2022/GDREcostat_2022.Rmd
gdr

---
title: "Infering species distribution from aggregated spatial data"
subtitle : "Going from coarse landings data to fine scale species distribution"
author : "Baptiste Alglave,  Marie-Pierre Etienne, Youen Vermard,  Mathieu Woillez, Etienne Rivot"

@@

\begin{columns}
\begin{column}{0.1\textwidth}
\center \Huge \textbf{\textcolor{BaptisteBlue}{\ding{58}}}
\normalsize
\end{column}
\begin{column}{0.3\textwidth}
\normalsize
Standardized sampling plan \\
High quality data
\end{column}
\begin{column}{0.3\textwidth}
Access to more data \\
Exact locations usually available
\end{column}
\begin{column}{0.3\textwidth}
Mandatory declaration \\
Massive data
\end{column}
\end{columns}

@@

\begin{columns}
\begin{column}{0.1\textwidth}
\center \Huge \fontsize{45}{15}{\textbf{\textcolor{BaptisteBlue}{-}}}
\normalsize
\end{column}
\begin{column}{0.3\textwidth}
\normalsize
Low amount of samples
\end{column}
\begin{column}{0.3\textwidth}
Opportunistic (or even preferential) sampling
\end{column}
\begin{column}{0.3\textwidth}
Aggregated at the scale of administrative units
\end{column}
\end{columns}

@@

\end{center}
\onslide<2>{
\footnotesize
\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Some specific proposition in the context of fishery science: \\
\tiny
Alglave Baptiste, Rivot Etienne, Etienne Marie-Pierre, Woillez Mathieu, Thorson James T, Vermard Youen (2022). \textbf{Combining scientific survey and commercial catch data to map fish distribution.} ICES Journal of Marine Science IN PRESS. \url{https://doi.org/10.1093/icesjms/fsac032}
\vspace{\baselineskip}
}

@@

\begin{columns}
\begin{column}{0.1\textwidth}
\center \tiny {\bf Resolution}
\end{column}
\begin{column}{0.45\textwidth}
\center \tiny Catch are daily declared at the resolution of ICES rectangles
\end{column}
\begin{column}{0.45\textwidth}
\center \tiny VMS pings are vessels GPS locations emitted each hour
\end{column}
\end{columns}
\tiny
\onslide<2>{
\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize \textbf{\textcolor{BaptisteBlue}{\ding{224}}  Refine landings spatial resolution}
\end{column}
\end{columns}
}

### Modelling change of support

@@

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{4cm} M{4cm} }
  \textcolor{BaptisteRed}{\textbf{Actual situation}} & 
  $Y_i | \textcolor{BaptisteBlue}{S}(x_i), x_i \sim \mathcal{L}_Y(\textcolor{BaptisteBlue}{S}(x_i),\xi,\sigma)$          &
  $Y_i=\textcolor{BaptisteRed}{Y_i^*}$ \\
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{2cm} M{4cm} M{2cm} }
  \textcolor{BaptisteLightGreen}{\textbf{Alternative solution}} & 
  $\textcolor{BaptisteLightGreen}{D_j}=\sum_{\textcolor{BaptisteLightGreen}{i \in \mathcal{P}_j}}{Y_{i}}$          &
  $\textcolor{BaptisteLightGreen}{D_j} | \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\textcolor{BaptisteLightGreen}{\mathcal{P}_j} \sim \mathcal{L}_D( \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\xi,\sigma)$
  & \textcolor{BaptisteBlue}{\ding{224}}  Match $\mathcal{L}_D$ and $\mathcal{L}_Y$ moments \\
  \end{tabular}
\end{table}

@@

\center
\textbf{Simulation/estimation}

@@

\end{column}
\begin{column}{0.55\textwidth}
\scriptsize
\textbf{Simulation}
\tiny
\begin{itemize}
\item \textcolor{BaptisteBlue}{\textbf{Latent field}} (\textcolor{BaptisteOrange}{covariate} + \textcolor{BaptisteBrown}{spatial random effect})
\item \textbf{Commercial data} (3000 samples over 2/3 of the area)
\item \textcolor{BaptisteLightGreen}{\textbf{Reallocation process}} (10 locations per declaration)
\item \textcolor{SurveyBlue}{\textbf{Scientific data}} (100 samples over the whole the area)
\end{itemize}

@@

\textbf{Estimation} \\
Comparison of 3 model configurations: \\
\tiny \vspace{\baselineskip} \scriptsize
1/ Model fitted to \textcolor{SurveyBlue}{scientific data} (reference data) \\
\tiny \vspace{\baselineskip} \scriptsize
2/ Integrated model with \textcolor{BaptisteRed}{commercial likelihood built on $Y_i^*$} \\
\tiny \vspace{\baselineskip} \scriptsize
3/ Integrated model with \textcolor{BaptisteLightGreen}{commercial likelihood built on $D_j$} \\
\tiny \vspace{\baselineskip}

@@

\scriptsize
\textbf{Model evaluation} \\
1/ Mean square prediction error \\
$$MSPE=\frac{\sum_x (\textcolor{BaptisteBlue}{S(x)} - \textcolor{BaptisteBlue}{\hat{S}(x)} ) ^2}{n}$$

@@

2/ Covariate effect (or species-habitat relationship): \\
$$\textcolor{BaptisteOrange}{\beta_S} = 2 \, \, \, \text{versus} \, \, \, \textcolor{BaptisteOrange}{\hat{\beta}_S}$$

@@

\begin{columns}
\begin{column}{0.5\textwidth}
\center
\includegraphics[width=2cm]{images/solea_solea.png}
\end{column}
\begin{column}{0.5\textwidth}
\tiny \textcolor{SurveyBlue}{\textbf{Survey data:}} Orhago\\
\textbf{Commercial data:} OTB-DEF traulers (to ease convergence onboard observer data were integrated in fitting)\\
\textbf{Fitted models:} same as simulation\\
\textcolor{BaptisteOrange}{\textbf{Covariate:}} substrate

@@

  Results_plot$obs <- NA
  Results_plot$obs[which(Results_plot$aggreg_obs == T)] <- "Dj"
  Results_plot$obs[which(Results_plot$aggreg_obs == F)] <- "Yi"
  Results_plot$obs[which(Results_plot$Estimation_model == 2)] <- "Scientific model"
  Results_plot$obs <- factor(Results_plot$obs,levels = c("Yi","Dj","Scientific model"))

@@

  beta_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = beta1_est,
                     fill = obs))+
    geom_hline(yintercept = 0,linetype="dashed")+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab(TeX("$\\beta_S$")) +
    xlab("")+
    geom_hline(yintercept = 2,col="red",linetype="dashed")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))

  MSPE_S_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = mspe,
                     fill = obs))+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab("MSPE")+xlab("")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    ylim(0,NA)

@@

  load("res/fit_IM_res_int_Yi.RData")
  int_Yi_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  int_Yi_plot <- ggplot(int_Yi_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Commercial likelihood on Yi")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

@@

### Case study: sole in the Bay of Biscay

@@

  ## Plot maps
  no.realloc_plot <- ggplot(no.realloc_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Commercial likelihood on Yi")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

@@

  ## Parameter estimates
  est_par_df_full_3$lkl <- factor(est_par_df_full_3$lkl,levels = c("Dj","Yi","Scientific model"))
  est_par_df_full_3 <- est_par_df_full_3 %>%
    filter(par_names != "substr_Sand_Coarse_substrate")
  par_plot <- ggplot(est_par_df_full_3, aes(y=par_val, x=par_names))+
    geom_point(
      aes(color = lkl),
      position = position_dodge(0.5),
      size=2
    )+
    geom_errorbar(aes(ymin = CI.inf, ymax = CI.sup, color = lkl),
                  position = position_dodge(0.5),width=0.4
    )+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    geom_hline(yintercept=0, linetype="dashed", color = "red",alpha=0.4)+
    xlab("")+ylab("")+
    theme_bw()+
    ggtitle("Parameters estimates")+
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),
          legend.title = element_blank(),
          legend.position = "bottom",
          aspect.ratio = 1)+
    coord_flip()+
    scale_x_discrete(labels=c('k_com'=parse(text = TeX('$k_{com}$')),
                              'Sigma_com'=parse(text = TeX('$\\sigma_{com}$')),
                              'q1_com'=parse(text = TeX('$\\xi_{com}$')),
                              'Sigma_sci'=parse(text = TeX('$\\sigma_{sci}$')),
                              'q1_sci'=parse(text = TeX('$\\xi_{sci}$')),
                              'Range'="Range",
                              'MargSD'="M. var.",
                              'substr_Mud_sediment'=parse(text = TeX('$\\beta_{S}$')),
                              'intercept'=parse(text = TeX('$\\mu$'))))

  ggsave("images/par_plot.png",width = 6,height = 7.5)

@@

\begin{center}
\includegraphics[width=5cm]{images/par_plot.png}
\end{center}
\tiny *n.b.: punctual commercial data (i.e. observer data) needed to be integrated in inference in order to make the model converge and some parmaters needed to be step estimated (e.g. range)

@@

\item Framework that integrates \textbf{catch declarations data} (rough resolution of catch) and \textbf{scientific/onboard observer data} (exact locations of catch) \\

@@

\textcolor{BaptisteBlue}{\ding{224}} \textbf{Still question:} how to ease convergence ? \\

@@

@@

\item \textbf{ Change of support issues } \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} not so frequent in spatial ecology, \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} but increasing amount of data available that may face such issues \\

@@

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} the overall approach is, \tiny \\ (i.e. modelling observed aggregagetd catches as a convolution of latent exact catches) \\ \vspace{\baselineskip} \normalsize

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} but need to adapt the observation model to the data \tiny \\ (here zeroinflated continuous data)   \\ \vspace{\baselineskip} \normalsize

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} and make the hypothesis that fishing locations ($\textcolor{BaptisteLightGreen}{\mathcal{P}_j}$) are known \scriptsize \\ (in reality $\textcolor{BaptisteLightGreen}{\mathcal{P}_j}$ is a trajectory and the set of fishing points are a realization of this trajectory) \\ \vspace{\baselineskip} \normalsize

@@

\begin{figure}
    \begin{tabular}{c c}
    \includegraphics[width=4.5cm]{images/peche_afrique_artisanale.jpg} &
    \includegraphics[width=4.5cm]{images/peche_artisanale.jpg} \\
    \includegraphics[width=4.5cm]{images/peche_hauturiere.jpg} &
    \includegraphics[width=4.5cm]{images/thon_rouge.jpg}
    \end{tabular}
\end{figure}

>>>>

---
title: "Infering species distribution from aggregated spatial data"
subtitle : "Going from coarse landings data to fine scale species distribution"
author : "Baptiste Alglave, Marie-Pierre Etienne, Kasper Kristensen, Youen Vermard,  Mathieu Woillez, Etienne Rivot"

@@

\begin{columns}
\begin{column}{0.1\textwidth}
\center \Huge \textbf{\textcolor{BaptisteBlue}{\ding{58}}}
\normalsize
\end{column}
\begin{column}{0.3\textwidth}
\normalsize
Standardized sampling plan \\
High quality data
\end{column}
\begin{column}{0.3\textwidth}
Access to more data \\
Exact locations available
\end{column}
\begin{column}{0.3\textwidth}
Mandatory declaration \\
Massive data
\end{column}
\end{columns}

@@

\begin{columns}
\begin{column}{0.1\textwidth}
\center \Huge \fontsize{45}{15}{\textbf{\textcolor{BaptisteBlue}{-}}}
\normalsize
\end{column}
\begin{column}{0.3\textwidth}
\normalsize
Small sample size
\end{column}
\begin{column}{0.3\textwidth}
Opportunistic (or even preferential) sampling
\end{column}
\begin{column}{0.3\textwidth}
Aggregated at the scale of administrative units
\end{column}
\end{columns}

@@

\end{center}
\onslide<2>{
\normalsize
\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Some specific application in the context of fishery science: \\
\scriptsize
\textit{Alglave Baptiste, Rivot Etienne, Etienne Marie-Pierre, Woillez Mathieu, Thorson James T, Vermard Youen (2022). \textbf{Combining scientific survey and commercial catch data to map fish distribution.} ICES Journal of Marine Science IN PRESS. \url{https://doi.org/10.1093/icesjms/fsac032}}
\vspace{\baselineskip}
}

@@

\begin{columns}
\begin{column}{0.1\textwidth}
\center \scriptsize {\bf Spatial \\ resolution}
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize Catch are daily declared at the resolution of ICES rectangles
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize VMS pings are vessels GPS locations emitted each hour
\end{column}
\end{columns}
\tiny
\onslide<2>{
\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize \textbf{\textcolor{BaptisteBlue}{\ding{224}}  Refine landings spatial resolution}
\end{column}
\end{columns}
}

### Two alternative procedures to reallocate catches

@@

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{4cm} M{4cm} }
  \textcolor{BaptisteRed}{\textbf{Current situation}} & 
  $Y_i | \textcolor{BaptisteBlue}{S}(x_i), x_i \sim \mathcal{L}_Y(\textcolor{BaptisteBlue}{S}(x_i),\xi,\sigma^2)$          &
  $Y_i=\frac{\textcolor{BaptisteLightGreen}{D_j}}{ \operatorname{n}(\textcolor{BaptisteLightGreen}{\mathcal{P}_j})}=\textcolor{BaptisteRed}{Y_i^*}$ \\
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{2cm} M{4cm} M{2cm} }
  \textcolor{BaptisteLightGreen}{\textbf{Alternative solution}} & 
  $\textcolor{BaptisteLightGreen}{D_j}=\sum_{\textcolor{BaptisteLightGreen}{i \in \mathcal{P}_j}}{Y_{i}}$          &
  $\textcolor{BaptisteLightGreen}{D_j} | \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\textcolor{BaptisteLightGreen}{\mathcal{P}_j} \sim \mathcal{L}_D( \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\xi,\sigma^2)$
  & \textcolor{BaptisteBlue}{\ding{224}}  Match $\mathcal{L}_D$ and $\mathcal{L}_Y$ moments \tiny (appendix) \\ 
  \end{tabular}
\end{table}

@@

\center
\textbf{Simulation-estimation}

@@

\end{column}
\begin{column}{0.55\textwidth}
\footnotesize
\textbf{Simulation}
\tiny
\begin{itemize}
\item \scriptsize \textcolor{BaptisteBlue}{\textbf{Latent field}} \tiny (\textcolor{BaptisteOrange}{covariate} + \textcolor{BaptisteBrown}{spatial random effect})
\item \scriptsize \textbf{Commercial data} \tiny (3000 samples over 2/3 of the area)
\item \scriptsize \textcolor{BaptisteLightGreen}{\textbf{Reallocation process}} \tiny (10 locations per declaration)
\item \scriptsize \textcolor{SurveyBlue}{\textbf{Scientific data}} \tiny (100 samples over the whole the area)
\end{itemize}

@@

\onslide<2-4>{
\footnotesize
\textbf{Estimation} \scriptsize \\
Comparison of 3 model configurations: \\
\tiny \vspace{\baselineskip} \scriptsize
1/ Model fitted to \textbf{\textcolor{SurveyBlue}{scientific data}} only \\
\tiny \vspace{\baselineskip} \scriptsize
2/ \textcolor{BaptisteDarkGrey}{\textbf{Integrated model}} (= \textbf{\textcolor{SurveyBlue}{scientific}} + \textbf{commercial data}) with \textcolor{BaptisteRed}{commercial likelihood built on $\bf{Y_i^*}$} \\
\tiny \vspace{\baselineskip} \scriptsize
3/ \textcolor{BaptisteDarkGrey}{\textbf{Integrated model}} with \textcolor{BaptisteLightGreen}{commercial likelihood built on $\bf{D_j}$} \\
\tiny \vspace{\baselineskip}

@@

\footnotesize
\textbf{Model evaluation} \scriptsize \\
1/ Mean square prediction error \\
$$MSPE=\frac{\sum_{x=1}^n (\textcolor{BaptisteBlue}{S(x)} - \textcolor{BaptisteBlue}{\hat{S}(x)} ) ^2}{n}$$

@@

2/ Covariate effect (or species-habitat relationship): \\
$$\textcolor{BaptisteOrange}{\beta_S} = 2 \, \, \, \text{versus} \, \, \, \textcolor{BaptisteOrange}{\hat{\beta}_S}$$
\vspace{\baselineskip}

@@

\begin{columns}
\begin{column}{0.5\textwidth}
\center
\includegraphics[width=2cm]{images/solea_solea.png}
\vspace{\baselineskip}
\vspace{\baselineskip}
\end{column}
\begin{column}{0.5\textwidth}
\tiny \textcolor{SurveyBlue}{\textbf{Survey data:}} Orhago\\
\textbf{Commercial data:} OTB-DEF trawlers (to ease convergence onboard observer data were integrated in the fit)\\
\textbf{Fitted models:} same as simulations\\
\textcolor{BaptisteOrange}{\textbf{Covariate:}} substrate

\normalsize \vspace{\baselineskip}

@@

  Results_plot$obs <- NA
  Results_plot$obs[which(Results_plot$aggreg_obs == T)] <- "Dj"
  Results_plot$obs[which(Results_plot$aggreg_obs == F)] <- "Yi*"
  Results_plot$obs[which(Results_plot$Estimation_model == 2)] <- "Scientific model"
  Results_plot$obs <- factor(Results_plot$obs,levels = c("Yi*","Dj","Scientific model"))

@@

  beta_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = beta1_est,
                     fill = obs))+
    geom_hline(yintercept = 0,linetype="dashed")+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab(TeX("$\\beta_S$")) +
    xlab("")+
    geom_hline(yintercept = 2,col="red",linetype="dashed")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))

  MSPE_S_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = mspe,
                     fill = obs))+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab("MSPE")+xlab("")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    ylim(0,NA)

@@

  load("res/fit_IM_res_int_Yi.RData")
  int_Yi_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  int_Yi_plot <- ggplot(int_Yi_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Commercial likelihood on Yi*")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

@@

### Case study: Sole in the Bay of Biscay

@@

  ## Plot maps
  no.realloc_plot <- ggplot(no.realloc_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Commercial likelihood on Yi*")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

@@

  ## Parameter estimates
  est_par_df_full_3$lkl[which(est_par_df_full_3$lkl == "Yi")] <- "Yi*"
  est_par_df_full_3$lkl <- factor(est_par_df_full_3$lkl,levels = c("Dj","Yi*","Scientific model"))
  est_par_df_full_3 <- est_par_df_full_3 %>%
    filter(par_names != "substr_Sand_Coarse_substrate")
  par_plot <- ggplot(est_par_df_full_3, aes(y=par_val, x=par_names))+
    geom_point(
      aes(color = lkl),
      position = position_dodge(0.5),
      size=2
    )+
    geom_errorbar(aes(ymin = CI.inf, ymax = CI.sup, color = lkl),
                  position = position_dodge(0.5),width=0.4
    )+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    geom_hline(yintercept=0, linetype="dashed", color = "red",alpha=0.4)+
    xlab("")+ylab("")+
    theme_bw()+
    ggtitle("Parameters estimates")+
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),
          legend.title = element_blank(),
          legend.position = "bottom",
          aspect.ratio = 1)+
    coord_flip()+
    scale_x_discrete(labels=c('k_com'=parse(text = TeX('$k_{com}$')),
                              'Sigma_com'=parse(text = TeX('$\\sigma_{com}$')),
                              'q1_com'=parse(text = TeX('$\\xi_{com}$')),
                              'Sigma_sci'=parse(text = TeX('$\\sigma_{sci}$')),
                              'q1_sci'=parse(text = TeX('$\\xi_{sci}$')),
                              'Range'="Range",
                              'MargSD'="M. var.",
                              'substr_Mud_sediment'=parse(text = TeX('$\\beta_{S}$')),
                              'intercept'=parse(text = TeX('$\\mu$'))))

  ggsave("images/par_plot.png",width = 6/1.75,height = 7.5/1.75)

@@

\begin{center}
\includegraphics[width=4.5cm]{images/par_plot.png}
\end{center}
\scriptsize
\onslide<2>{

The \textcolor{BaptisteDarkGrey}{\textbf{integrated model}} fitted to \textcolor{BaptisteLightGreen}{$\bf{D_j}$}:

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Recovers the species-habitat relationship ($\bf{\textcolor{BaptisteOrange}{\beta_S}}$)

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Modifies the \textbf{contrasts of the map} \tiny (shape and intensity of the hotspots/coldspots) \scriptsize

@@

\item \textcolor{BaptisteDarkGrey}{\textbf{Integrated framework}} that combines \textcolor{BaptisteLightGreen}{\textbf{catch declarations data}} (rough resolution) and \textcolor{SurveyBlue}{\textbf{scientific data}} (exact locations) \\
\textcolor{BaptisteBlue}{\ding{224}} Allows to estimate the \textcolor{BaptisteOrange}{\textbf{habitat effect}} through commercial data \\
\textcolor{BaptisteBlue}{\ding{224}} Modifies the \textbf{contrasts of the map} (hotspots vs. coldspots)

\tiny \vspace{\baselineskip} \normalsize

@@

\item \textbf{Some limits:}

\textcolor{BaptisteBlue}{\ding{224}} How to ease convergence ? \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Need to make the hypothesis that fishing locations ($\textcolor{BaptisteLightGreen}{\mathcal{P}_j}$) are known

@@

\tiny \vspace{\baselineskip} \normalsize

@@

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} The overall approach is, \scriptsize \\ \textit{(i.e. modelling observed aggregated observations as a sum of latent punctual observations)}

\normalsize \textbf{\textcolor{BaptisteBlue}{\ding{224}}} But need to adapt the observation model to the data \scriptsize \\ \textit{(here zeroinflated positive continuous data)}

@@

\item \textbf{ Change of support applications} \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Increasing amount of available data that may face such issues \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Here is one proposition to integrate aggregated data in SDM \\

@@

\begin{figure}
    \includegraphics[width=11cm]{images/front_page.png}
\end{figure}

\footnotesize

\textbf{Punctual observation model} ($Y_i$):

\scriptsize $\operatorname{L}(y,\mu,\sigma^2)$ is the lognormal likelihood for observation $y$, mean $\mu$ and variance $\sigma^2$

$Y$ and $D$ are supposed conditional on S and x \footnotesize

$$
\operatorname{P}\left(Y_i=y_{i} \right) =
\left\{
    \begin{array}{ll}
        p_i & \text { if } y_{i}=0 \\
        \left(1-p_i\right) \cdot \operatorname{L}\left(y_{i },\mu_i=\frac{S(x_i)}{\left(1 - p_i\right)},\sigma^{2} \right) & \text { if } y_{i} > 0
    \end{array}
\right.
$$

$$p_{i}=\exp(-e^\xi .S(x_{i}))$$

\tiny \vspace{\baselineskip} \footnotesize

\textbf{Declaration model} ($D_j=\sum_{i \in \mathcal{P}_j}{Y_{i}}$):

\begin{align*}
P(D_j = 0) & = \prod_{i\in \mathcal{P}_j} P(Y_{i} = 0)
                      = \exp{ \left \lbrace- \sum_{i\in \mathcal{P}_j} e^{\xi}. S(x_{i})\right \rbrace} = \pi_j.
\end{align*}

$$\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) =  \operatorname{L}\left(d_{j},\mu_j = E(D_j|d_j>0),\sigma_j^2 = ln(\frac{Var(D_j|d_j>0)}{E(D_j|d_j>0)^2} + 1) \right)$$

$$E(D_j \vert d_j > 0)=\frac{\sum_{i \in \mathcal{P}_j} S(x_{i})}{1-\pi_j}$$

$$Var(D_j \vert d_j > 0) = \frac{\sum_{i \in \mathcal{P}_j} Var(Y_{i})}{1-\pi_j} - \frac{\pi_j}{(1-\pi_j)^2}E(D_j)^2$$

$$Var(Y_{i})=\frac{S(x_{i})^2}{1-p_{i}}(e^{\sigma^2}-(1-p_{i}))$$
